\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Elaboration}
\author{jack.mathieson }
\date{August 2019}

\begin{document}

\maketitle

\tableofcontents
\section{Introduction}
This Elaboration is meant to outline the goals, requirements and possible technical processes of my future MRes Thesis. Pains, gains and possible solutions have been posited in two earlier scoping papers. 

\section{Thesis Vision}
The thesis I plan to write will be on narrative construction by Iranian Refugees living in Sydney. It will examine the ways narratives are expressed and built by these people and will take an emic perspective, attempting to introduce the topic from their own view of it. The primary method used in Anthropology to capture such a perspective is Ethnography, which utilizes extensive participant-observation and relational, qualitative research rather than quantitative analysis. Words and their significance, context and it's situation, agency and it's ownership: it is this kind of data and meta-data that will be most useful, so a system of analysis that can cope with data of this nature is necessary.
    
\section{ Scoping Results}

The results of the past scoping papers identified an area where significant time-constraints are placed on the ethnographic process: transcribing interviews. As interviews are (one of) the best methods of capturing complex, qualitative data they will be used frequently throughout the research process. The disadvantage of this approach is that for every hour spent interviewing a participant there are at \textit{least} three hours of transcribing, often more. This takes up valuable time that might otherwise be spent in participant-observation, which is possibly the primary way
Ethnography is conducted.

As such, scoping revealed that the most useful tool for ethnographic research that involves multiple interviews would be an audio recording tool that can perform the following:
\begin{enumerate}
\item Record and segment a continuous stream of sound.
\item Provide a means of storing meta-data for each recorded stream.
\item Shift and re-organize selected segments of sound while retaining a copy of the original stream.
\item Be able to identify sounds that correspond to words and transcribe these.
\item The recorder must be able to record a specific, non-audible signal that can be delivered on command and recorded alongside the stream of sound. The connection may be via blue-tooth or any form of wireless connection provided the recorder can record it alongside the audible sound-stream*.
\end{enumerate}

\textbf{*Note on Scoping point 5}: this requirement is for the purpose of identifying a key moment in an interview. The ideal tool would be a small "button" that the interviewer can soundlessly click at any point in the interview when something particularly meaningful had been said. If this soundless signal is recorded alongside the audio-stream then the interviewer need only listen to the segment of recording containing that signal rather than scroll through the whole recording for "that moment" they remember hearing.

In addition to this, the tool would need to have a simple way of transferring the recorded file from the audio recorder to a computer. Alternatively if the physical audio recorder has built-in software or downloadable software that can be installed on a computer this would also be sufficient.

\section{Incompatible Tools}
A simple recording of a stream of sound is insufficient, so most standard Windows Media programs would not help. While such programs can accurately capture a single stream of sound and even cut and shuffle segments of the recording, they cannot meet the requirements listed in points 2, 4 and 5.

Additionally, a tool that can record and transcribe is still not enough. Even if the level of accuracy is insufficient, as is usually the case for programs like the YouTube transcription tool, one sitting of listening to the recording will pick up on such mistakes. The key here is that even with a pin-point accurate transcription tool, like Transcribe, such a program is still only designed to pick up on \textit{audible} data, which does not meet point 5.

Furthermore, a tool that can record audible  \textit{and} an inaudible, electronic signals rarely has transcribing capabilities as well. A software used in music recording and creation might have the capacity for picking up on an inaudible Bluetooth signal, and would be perfect as a visual tool that can reorganize and copy different streams, however it still would not solve the issue of discerning words from sound and writing them down.

And finally there is the issue of a convenient, simple file-transfer process from recorder to computer. A useful feature of the Roland R-26 Digital Field Audio Recorder is that it comes equipped with a USB port, making file-transfer simple. Unfortunately this does not solve the issue of point 5, as the recorder, while being able to record multiple \textit{audible} streams, cannot pick up on non-audible signals.

\section{Possible Tool Application}
As outlined before, the ideal tool would be a program that can record both streams of sound and inaudible signals, reorganize and transcribe those streams. One potential way of bringing all of these facets together would be to have two different tools working together: a recorder and a transcriber software. The recorder must be able to pick up on audible sounds and inaudible signals, and whatever format it then presents them in on a computer must include both the audible and inaudible recordings. However the Transcribing tool need only transcribe the audible sounds, not the inaudible signals. Thus, the only requirement of the Transcribing tool is that it be a software compatible with whatever format the recording tool delivers the audio file in to the computer.

\section{Concluded Plan}
In line with the above requirements and possible applications,  this elaboration desires the following tools: 
\begin{enumerate}
\item An audio recorder of the same quality used in music creation which can record inaudible, wireless signals
\item A transcriber software that is compatible with the audio-file format produced by the audio recorder.
\end{enumerate}

\section{Testing}

There are two components to test: the audio recorder device and the transcribing software. What follows is the plan to test each component for its suitability.

\subsection{Transcribing Software Test and Results:}
The testing process here was a simple search and application of various online transcribing tools on offer. Four different programs were tested: Otranscribe, Transcribe, Trint and Happyscribe. A media file of a song was uploaded to each and then transcribed; the same song was applied to each program. Most were able to upload the file without difficulty, meeting one specification, however of the four only Transcribe was able to accurately transcribe the song lyrics. The other programs made mistakes so frequently that the work of editing the transcription would defeat the purpose of the tool. 

One unforeseen disadvantage of using Transcribe is that because it is an online service there is a fee for its use. The program was able to accurately transcribe the first 60 seconds of the words from a song that most other program found virtually impossible to interpret, however for it to transcribe further would cost \$6 per hour of machine transcription. Over a period of months this would likely add up to \$120 at only 20 hours worth of recordings, and this is not including the \$20 annual fee for self-subscription. Over a five month project this would then result in a \$140 cost just for collecting and storing data. However, the benefit is that for the same recording time it would take off two to three hours of transcription time, essentially buying 40 to 60 hours of work for the price of \$140.

One further test that needs to be conducted with Transcribe before it would be considered appropriate for use would be how well it interprets the audio file produced by the selected audio recorder.

\subsection{Audio Recorder Test and Results:}

Based on recommendations the Zoom H4n Audio Recorder was chosen to test. In the absence of the physical recorder a preliminary test was conducted on the device manual to see if the instructions were useful and if the device was built for the desired purpose. A basic check-list of fifteen, project-specific criteria was made, including basic criteria such as how to turn the device on and off, playback capabilities, saving and storage and transferring audio files between devices. 
	
    All but two criteria were met, the last two unconfirmed. Firstly, the instructions for pausing and resuming recording are not distinguished well enough from the instructions that describe how to pause and resume a playback. Second, the manual did not specify if the marks that could be made during playback and saved on the device would be transferred with the converted MP3 file that would be transcribed on a computer. Both these will only be confirmed as negative results once a test has been conducted on the actual device. 
    
\subsection{MP3 Transcription Test and Results}
Having ascertained that the H4n Recorder transfers files in the MP3 format a simple test was run on Transcribe's ability to interpret an MP3 file. It produced a nearly perfect written account. Only a handful of errors were transcribed from the first 60 seconds of a past lecture that included background noise and a fluctuating tone. 
	
    Unfortunately, the H4n's capability to transfer marks with the MP3 file to a computer is essential for this project, and so if the test on the physical device does produce a negative then the Zoom H4n may prove to be the wrong tool for this project.
    
\subsection{Zoom H4n Audio Recorder Test and Results}
Based off of the preliminary manual test the physical audio recorder was tested for its capabilities, being run through an amended version of the manual check-list. The primary goal of this test was to see how the "marks" created on the recording device would translate as an MP3 file on a computer. 
	
    The recorder itself operated as expected and with successful results. The file it transferred to the computer was read as a standard windows media file and Transcribe was able to interpret it with minimal mistakes. The device also produced the desired effect with its "mark" function. On the device, each mark could be skipped to using the next-section keys. Unfortunately, these marks were not recorded in any practical way on the transferred audio file, registering only as the background noise of a button being pressed. This, unfortunately, means that the only way to meaningfully find the marked points is to bring up the "marks list" application on the device, which records the minute and second that a mark was made in a recording.
    
    It is possible to have both  the device and a computer operate at the same time so as to hear the transcribed recording as well as know what time to skip to for each mark, however this is a cumbersome process and could be substituted for a simple pen and note-pad that recorded minutes of interest.
    
    The one advantage of the H4n recorder is that can record sound exceptionally clearly. This would make the transcription process much simpler for both automatic and human transcription.


\end{document}
